---
title: "3_Experiment_Analysis"
format: html
editor: visual
---

## Load Packages and Data

```{r LoadPackages, include=FALSE}
### LOAD PACKAGES
# Load packages using pacman
pacman::p_load(tidyverse,    # A meta-package of data manipulation tools
               ggdist,       # Additional geoms for plotting visualizations
               lme4,         # For fitting mixed effect models
               lmerTest,     # For p-values on mixed effect models
               emmeans,      # For estimated marginal means and contrasts
               pwr,          # For power analyses
               corrplot,     # Correlation plot package
               psych,        # A range of tests; this script uses corr.test
               modelsummary, # Presents outputs of regression models
               effectsize,   # Model interpretation tools
               gt,           # For making tables
               gtsummary,    # Makes summary tables
               gridExtra,    # For arranging plots
               patchwork,    # For arranging plots
               here)         # A package for managing filepaths in a flexible way

### SET UP RELATIVE FILEPATHS WITH HERE PACKAGE
# Identify the file location
here::i_am("AI_Decision_Quality_Code.qmd")

### SET THEME FOR PLOTS
theme_jdc <- function() {
  theme(plot.title = element_text(hjust=0.5, face="bold"),
              plot.subtitle = element_text(hjust=0.5),
              plot.background=element_rect(fill="#ffffff"),
              panel.background=element_rect(fill="#f9f5eb"),
              panel.grid.minor=element_blank(),
              panel.grid.major.y=element_blank(),
              panel.grid.major.x=element_line(),
              axis.ticks.length = unit(.25, "cm"),
              axis.title.y = element_text(angle = 0, vjust=0.5),
              legend.position="bottom",
              legend.background = element_rect(fill="transparent", colour=NA),
              legend.key = element_rect(fill="transparent", colour=NA))
  }

# Function to generate n=numcolors hex codes from a colorblind-friendly pallet
theme_paultol_colors <- function(numcolors) {
  color_choices = c("darkblue", "#228833", "#DDAA33", "#BB5566", "#44AA99", "#66CCEE", "#999933")
  return(color_choices[1:numcolors])
}

### HELPER FUNCTIONS
# Rounds number to three digits for prettier tables
round_to_three <- function(x){round(x, digits = 3)}
```

### Load Data

Data is prepared by the separate ETL script file.

```{r LoadData}
exp1_data <- readRDS(here::here("Data", "Experiment_1_Data_Preprocessed.rds")) |>
  mutate(Experiment = "Experiment 1",
         Quality = factor(if_else(Explanation == "No AI", "NA", "High"),
                          levels = c("NA", "Low", "High")),
         Role = if_else(Role %in% c("Midlevel Provider", "Nurse"), "Other", Role)) |>
  filter(!str_detect(Explanation, "Conf")) |> # Remove the "confidence" conditions
  filter(!is.na(DistanceFinal))

exp2_data <- readRDS(here::here("Data", "Experiment_2_Data_Preprocessed.rds")) |>
  mutate(Experiment = "Experiment 2") |>
  mutate(Quality = factor(if_else(Explanation == "No AI", "NA", Quality),
                          levels = c("NA", "Low", "High")),
         Role = if_else(Role %in% c("Midlevel Provider", "Nurse"), "Other", Role))

exp3_data <- readRDS(here::here("Data", "Experiment_3_Data_Preprocessed.rds")) |>
  mutate(Experiment = "Experiment 3") |>
  mutate(Quality = factor(if_else(Explanation == "No AI", "NA", Quality),
                          levels = c("NA", "Low", "High")),
         
         Role = if_else(Role %in% c("Midlevel Provider", "Nurse"), "Other", Role))
```

## Outlier Analysis

We do not remove outliers, in the interest of a conservative analysis, but we did look at them. Results aren't substantially different if they are removed.

### Experiment 1

```{r}
### Flag values greater than 10mg from correct answer as outliers and remove NAs
exp1_data <- exp1_data |>
  filter(!is.na(DistanceFinal)) |>
  mutate(Outlier = DistanceFinal >= 10)

### Plot Data
exp1_data |> ggplot(aes(x = Scenario, y = DistanceFinal, color = Outlier)) +
  geom_jitter() +
  facet_grid(~ Explanation)


```

### Experiment 2

```{r}
### Flag items >= 7mg from correct answer or whose WoA is greater than 1
exp2_data <- exp2_data |>
  mutate(Outlier = (DistanceFinal >=7 |
                   (WeightOnAdvice > 1 & !is.na(WeightOnAdvice)) |
                    WeightOnAdvice < 0 | is.infinite(WeightOnAdvice))
         )

### Plot Initial and Final Distance
exp2_data |>
  ggplot(aes(x = Scenario, y = DistanceInitial, color = Outlier)) +
  geom_jitter() +
  facet_grid(Explanation ~ Quality)

exp2_data |>
  ggplot(aes(x = Scenario, y = DistanceFinal, color = Outlier)) +
  geom_jitter() +
  facet_grid(Explanation ~ Quality)

exp2_data |>
  ggplot(aes(x = Scenario, y = WeightOnAdvice, color = Outlier)) +
  geom_jitter() +
  facet_grid(Explanation ~ Quality)
```

### Experiment 3

```{r}
exp3_data |> 
  mutate(Sc = if_else(Scenario == 1, "Starting Dose 7.5mg, Correct Dose 5.5mg",
                      "Starting Dose 11mg, Correct Dose 9mg")) |>
  ggplot(aes(x = Explanation, y = InitialDose)) +
  geom_jitter(aes(color = Quality), alpha = 0.5) +
  geom_hline(aes(yintercept = CorrectDose)) +
  geom_hline(aes(yintercept = StartingDose), linetype = 3) +
  scale_color_manual(values = theme_paultol_colors(2)) +
  facet_wrap(~ Sc) +
  theme_jdc()

## Erroneous/Inconsistent Use of Advice
exp3_data |>
  mutate(Sc = if_else(Scenario == 1, "Starting Dose 7.5mg, Correct Dose 5.5mg",
                      "Starting Dose 11mg, Correct Dose 9mg")) |>
  ggplot(aes(x = Explanation, y = WeightOnAdvice)) +
  geom_jitter(alpha = 0.5) +
  facet_wrap(~ Quality) +
  theme_jdc()

# The three responses with negatives Weight on Advice actually could be using the low-quality advice to improve their decisions (and two of them do...). Evaluating the low-quality recommendation could be helping them reevaluate the factors.

exp3_data <- exp3_data |>
  mutate(Outlier = case_when((Scenario == 1 & InitialDose > 8)  ~ TRUE,
                             (Scenario == 2 & InitialDose > 12) ~ TRUE,
                             WeightOnAdvice > 1 | WeightOnAdvice <0 ~ TRUE,
                             TRUE ~ FALSE))

table(exp3_data$Outlier)
```

## Combine Dataframes

This is used for generating the summary stats.

```{r}
columns_to_select <- c("Experiment", "Scenario", "ResponseId", "Role", "Age", "Gender", "Physician",
                       "YearsExperience", "Explanation", "CorrectDose", "Quality",
                       "DistanceFinal", "EmotionalTrust", "Outlier")

exp123_df <- rbind(
  exp1_data |> select(all_of(columns_to_select)),
  exp2_data |> select(all_of(columns_to_select)),
  exp3_data |> select(all_of(columns_to_select))
) |>
  mutate(Gender = factor(Gender,
                         levels = c("Male", "Female",
                                    "Non binary / transgender / third gender",
                                    "Not Recorded")),
         Explanation = factor(Explanation,
                              levels = c("No AI", "Global", "What", 
                                         "What + Why", "What + Why + How")))

write_csv(exp123_df, here("Data", "Experiments123_Combined_Data.csv"))
```

## Summary Stats

Generate a Summary Stats Table

```{r}
## Summary Table
summary_stats_table <- tbl_summary(
  data = exp123_df |>
    group_by(ResponseId) |>
    slice_head() |>
    ungroup() |>
    select(Role, YearsExperience, Age, Gender, -ResponseId, Experiment),
  by = Experiment,
  type = c(Age ~ "continuous",
           YearsExperience ~ "continuous"),
  missing_text = "No Answer"
)

### Display Table
summary_stats_table

### Save to word
summary_stats_table |> 
  as_gt() |> 
  gt::gtsave(filename = here::here("tbl_summary_stats.docx"))

```

## Experiment 1

### Exp1 Manipulation Check

```{r}
### Manipulation Check
exp1_ManipCheck_df <- exp1_data |> 
  group_by(ResponseId) |>
  filter(row_number() == 1 & Recommendation ==1) |>
  select(Reasoning, MeanReasoning) |>
  ungroup()

exp1_ManipCheck_df |>
  group_by(Reasoning) |>
  summarize(GroupMeanReasoning = mean(MeanReasoning, na.rm = TRUE),
            n = n())

anova(lm(MeanReasoning ~ Reasoning, data = exp1_ManipCheck_df))

### AI vs Control
lm(DistanceFinal ~ Recommendation, exp1_data) |> summary()
```

### Exp1 Decision Quality between Scenarios

```{r}
### Decision Quality between Scenarios
exp1_data |>
  filter(!Outlier & Explanation != "No AI") |>
  group_by(Scenario) |>
  summarize(n = n(),
            mean = mean(DistanceFinal, na.rm = TRUE),
            se = sd(DistanceFinal, na.rm = TRUE)/sqrt(n))

# Test for differences by scenario
t.test(DistanceFinal ~ Scenario, data = exp1_data |> filter(!Outlier & Explanation != "No AI"))
```

### Exp1 ANOVA

```{r}
### Run linear regressions for Experiment 1
# Only include the AI conditions (don't include base NO AI)
# Decision Quality
exp1_dist_lm <- lmer(DistanceFinal ~ Explanation * Role + (1|ResponseId),
        data = exp1_data |> filter(Explanation != "No AI"))

print("Decision Quality (Final Distance in mg)")
anova(exp1_dist_lm)

# Emotional Trust
exp1_trust_lm <- lm(EmotionalTrust ~ Explanation * Role, 
        data = exp1_data |> filter(Explanation != "No AI" & Scenario == 1))

print("Emotional Trust")
anova(exp1_trust_lm)
```

#### Exp1 ANOVA Tables

```{r}
### ANOVA Table formatting in APA style
# Overall decision quality and just AI conditions
rbind(anova(exp1_dist_lm) |>
        rename(p.value = `Pr(>F)`) |>
        cbind(effectsize::eta_squared(exp1_dist_lm, partial = TRUE)) |>
        mutate(DV = "Decision Quality - Just AI",
               stars = gtools::stars.pval(p.value)),
      anova(exp1_trust_lm) |>
        rename(p.value = `Pr(>F)`) |>
        cbind(rbind(
          effectsize::eta_squared(exp1_trust_lm, partial = TRUE),
          NA)) |> # No Partial eta Sq for the residuals row
        mutate(DV = "Trust",
               stars = gtools::stars.pval(p.value),
               DenDF = 76) |>
        rename(NumDF = Df)
      ) |>
  mutate_if(is.numeric, round_to_three) |>
  mutate(p.value = paste(p.value, stars)) |>
  select(DV, Parameter, `Sum Sq`, NumDF, DenDF, `Mean Sq`,
         `F value`, p.value, Eta2_partial) |>
  gt() |>
  gtsave(here("tbl_Exp1_TABLE_S1.docx"))

```

### Exp1 Figure

```{r}
### Experiment 1 Figure - Decision Quality

exp1_fig_data <- exp1_data |>
  filter(!Outlier & !is.na(Role) & Explanation != "No AI") |>
  group_by(Role, Explanation) |>
  summarize(n = n(),
            mean = mean(DistanceFinal, na.rm = TRUE),
            se = sd(DistanceFinal, na.rm = TRUE)/sqrt(n)) |>
  mutate(Explanation = factor(if_else(Explanation == "What", "Local\nWhat", Explanation),
                              levels = c("No AI", "Global", "Local\nWhat")))

fig_exp1_decision_quality <- exp1_fig_data |>
  ggplot(aes(x = Role,
             y = mean,
             color = Explanation,
             ymin = mean - 1.96 * se,
             ymax = mean + 1.96 * se)) +
    geom_pointrange(position = position_dodge(0.4)) +
    scale_color_manual(values = c("Global" = "darkblue",
                                  "Local\nWhat" = "#228833")) +
    scale_x_discrete(labels = c("Other" = "Midlevel\nor Nurse", "Pharmacist" = "Pharmacist", "Physician" = "Physician")) +
    labs(y = "Distance (mg) from\nCorrect Dose\n(Lower is better)",
         x = "",
         color = "AI Explanation") +
    #scale_y_continuous(limits = c(0, 3.5)) +
    theme_jdc() +
    theme(axis.title.y = element_text(angle = 0),
          axis.ticks.y = element_blank())

# Save the figure
ggsave(here::here("fig_exp1.png"), fig_exp1_decision_quality, width = 5, height = 3)
```

### Exp1 Trust - Quality Correlation

```{r}
corr_exp1 <- corr.test(exp1_data |>
            filter(!Outlier & (Explanation != "No AI")) |>
            select(EmotionalTrust, DistanceFinal))

print(paste0("r(",corr_exp1$n-2,") = ",
             round(corr_exp1$r[1,2], 2),
             ", p=",
             round(corr_exp1$p[1,2], 4)))
```

## Experiment 2

### Exp2 Individual Movement Plot

```{r}
movt_df <- exp2_data |>
  group_by(Scenario, Quality, Explanation) |>
  filter(InitialDose <= 12 & !Outlier) |>
  arrange(InitialDose, Movement, .by_group = TRUE) |>
  mutate(CorrectDose = if_else(CorrectDose == 4,
                                 "Scenario 1, Correct Dose 4mg",
                                 "Scenario 2, Correct Dose 1.5mg"),
         Quality = if_else(Quality == "Low", "Low Quality Rec", "High Quality Rec"),
         Explanation = if_else(Explanation == "Global", "Global", "Global + Local What")
  )


movt_df$rowID = as.numeric(rownames(movt_df))

movt_df <- movt_df |>
  ungroup() |>
  group_by(CorrectDose, Quality) %>%
  mutate(rowID = rowID - min(rowID)) |>
  ungroup()

movt_df_labels <- tribble(
  ~text,         ~Quality,             ~CorrectDose,                        ~x,    ~y, ~label_hjust,
  "AI\nRecc",     "Low Quality Rec",    "Scenario 1, Correct Dose 4mg",  8.25, 5, 0,
  "AI\nRecc",     "Low Quality Rec",    "Scenario 2, Correct Dose 1.5mg",    4.65,    5, 0,
  "Patient's\nPrior\nDose", "High Quality Rec","Scenario 1, Correct Dose 4mg",6.25, 80, 0,
  "Patient's\nPrior\nDose", "High Quality Rec","Scenario 2, Correct Dose 1.5mg",3.15,80,0
  )

fig_exp2_individualmovt <- ggplot() +
  geom_vline(data = movt_df,
             aes(xintercept = if_else(CorrectDose == "Scenario 1, Correct Dose 4mg",
                                      4, 1.5)),
             color = "gray40") +
  geom_vline(data = movt_df,
             aes(xintercept = AIDose), color = "gray40", linetype = 2) +
  geom_vline(data = movt_df,
             aes(xintercept = StartingDose), color = "gray40", linetype = 3) +
  geom_point(data = movt_df,
             aes(x = InitialDose,
                 y = rowID,
                 color = Explanation),
             size = 1) +
  geom_point(data = movt_df |> filter(InitialDose != FinalDose),
             aes(x = FinalDose,
                 y = rowID,
                 color = Explanation),
             size = 2) +
  geom_segment(data = movt_df %>%
                 filter(InitialDose - FinalDose > 0),
               aes(x = InitialDose, xend = FinalDose+0.1,
                   y = rowID, yend = rowID),
               arrow = arrow(length = unit(0.02, "npc")),
               color = "gray20") +
  geom_segment(data = movt_df %>%
                 filter(InitialDose - FinalDose < 0),
               aes(x = InitialDose, xend = FinalDose-0.1,
                   y = rowID, yend = rowID),
               arrow = arrow(length = unit(0.02, "npc")),
               color = "gray20") +
  geom_text(data = movt_df_labels, aes(x = x, y = y, label = text),
            color = "gray20", hjust = movt_df_labels$label_hjust) +
  labs(title = "Individual Decision Adjustment Plot",
       y = "",
       x = "Dose Selected (mg)",
       color = "Explanation Condition") +
  scale_color_manual(values = theme_paultol_colors(3)) +
  scale_x_continuous(breaks = seq(0, 12, 2)) +
  theme_jdc() +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5),
        axis.text.y = element_blank(),
        axis.text.x = element_text(size = 12),
        axis.ticks.y = element_blank(),
        plot.title = element_text(size = 16),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12)) +
  facet_grid(Quality ~ CorrectDose, scales = "free_x")

# Export
ggsave(here::here("fig_exp2_IndividualMovt.png"), fig_exp2_individualmovt, width = 6.5, height = 8)
```

### Exp2 Differences by Scenario

```{r}
# Mean Distance from Correct Dose by Scenario
exp2_data |>
  filter(!Outlier) |>
  group_by(Scenario) |>
  summarize(n = n(),
            mean = mean(DistanceFinal, na.rm = TRUE),
            se = sd(DistanceFinal, na.rm = TRUE)/sqrt(n))

# Test for differences by scenario
t.test(DistanceFinal ~ Scenario, data = exp2_data |> filter(!Outlier))
```

### Exp2 Qual Analysis

```{r}
### Summarize by median
exp2_qual_table <- exp2_data |>
  filter(!Outlier) |>
  group_by(Quality) |>
  summarize(n = n(),
            Changed = sum(AbsMovement > 0),
            PctChange = scales::percent(Changed/n, accuracy = 0.1),
            Improved = sum(Improvement > 0),
            PctImproved = scales::percent(Improved/Changed, accuracy = 0.1),
            Increased = sum(Movement > 0)) |>
  ungroup() |>
  rename(`No. Obs.` = n) |>
  mutate(`Changed (%)` = paste0(Changed, " (", PctChange, ")"),
         `Improved (%)` = paste0(Improved, " (", PctImproved, ")")) |>
  select(-Changed, -PctChange, -Improved, -PctImproved) |>
  flextable::regulartable() |>
  flextable::autofit()

### Export the Table to a Word Doc for Pasting
word_document_name <-
    officer::read_docx() |>
    flextable::body_add_flextable(exp2_qual_table) |>
    print(target = here::here("tab_exp2_qualtable_TABLE_S3.docx"))
```

### Exp2 ANOVA

```{r}
### Run Linear Regressions to then conduct ANOVA
# Final Decision Quality
exp2_dist_lm <- lmer(DistanceFinal ~ Explanation + Quality + Role +
+        Explanation:Quality + Explanation:Role + Quality:Role + (1|ResponseId), 
        data = exp2_data)

print("Decision Quality (Final Distance in mg)")
anova(exp2_dist_lm)

# AI Influence measured as Absolute Movement
exp2_movt_lm <- lmer(AbsMovement ~ Explanation + Quality + Role +
+        Explanation:Quality + Explanation:Role + Quality:Role + (1|ResponseId), 
        data = exp2_data)

print("Absolute Movement (Distance in mg)")
anova(exp2_movt_lm)

# Emotional Trust
exp2_trust_lm <- lmer(EmotionalTrust ~ Explanation + Quality + Role +
+        Explanation:Quality + Explanation:Role + Quality:Role + (1|ResponseId), 
        data = exp2_data)

print("Emotional Trust")
anova(exp2_trust_lm)

# Emotional Trust by Quality
exp2_trust_lowqual <- lm(EmotionalTrust ~ Explanation*Role, 
        data = exp2_data |> filter(Quality == "Low"))
print("Emotional Trust - Low Quality Only")
anova(exp2_trust_lowqual)

exp2_trust_hiqual <- lm(EmotionalTrust ~ Explanation*Role, 
        data = exp2_data |> filter(Quality == "High"))
print("Emotional Trust - High Quality Only")
anova(exp2_trust_hiqual)



# Weight On Advice
exp2_WoA_lm <- lmer(WeightOnAdvice ~ Explanation + Quality + Role +
        Explanation:Quality + Explanation:Role + Quality:Role + (1|ResponseId), 
        data = exp2_data |> filter(!(is.na(WeightOnAdvice) | is.infinite(WeightOnAdvice))))

anova(exp2_WoA_lm)

# Power analysis for WoA Explanation/Quality
emm <- emmeans(exp2_WoA_lm, ~ Explanation * Quality)
pairs_df <- as.data.frame(pairs(emm, adjust = "tukey"))
sigma_model <- sigma(exp2_WoA_lm) # Residual SD from the model
n_per_cell  <- mean(table(exp2_data$Quality, exp2_data$Explanation)[2:3,])
alpha_adj   <- 0.05 / nrow(pairs_df)

pairs_df$cohens_d <- pairs_df$estimate / sigma_model

pairs_df$power <- mapply(function(d, se) {
  pwr.t.test(n = n_per_cell, d = abs(d),
             sig.level = alpha_adj, type = "two.sample")$power
}, pairs_df$cohens_d, pairs_df$SE)

pairs_df$n_needed <- sapply(pairs_df$cohens_d, function(d) {
  ceiling(pwr.t.test(d = abs(d), sig.level = alpha_adj,
                     power = 0.80, type = "two.sample")$n)
})
pairs_df # Show the results; n_needed is *per cell*

```

#### Exp2 ANOVA Tables

Then build and export tables.

```{r}
### ANOVA Table formatting in APA style
rbind(anova(exp2_dist_lm) |>
        rename(p.value = `Pr(>F)`) |>
        cbind(effectsize::eta_squared(exp2_dist_lm, partial = TRUE)) |>
        mutate(DV = "Decision Quality",
               stars = gtools::stars.pval(p.value)),
        
      anova(exp2_movt_lm) |>
        rename(p.value = `Pr(>F)`) |>
        cbind(effectsize::eta_squared(exp2_movt_lm, partial = TRUE)) |>
        mutate(DV = "Decision Change",
               stars = gtools::stars.pval(p.value)),

      anova(exp2_trust_lm) |>
        rename(p.value = `Pr(>F)`) |>
        cbind(effectsize::eta_squared(exp2_trust_lm, partial = TRUE)) |>
        mutate(DV = "EmotionalTrust",
               stars = gtools::stars.pval(p.value))
      ) |>
  mutate_if(is.numeric, round_to_three) |>
  mutate(p.value = paste(p.value, stars)) |>
  select(DV, Parameter, `Sum Sq`, NumDF, DenDF, `Mean Sq`,
         `F value`, p.value, Eta2_partial) |>
  rbind(c(DV = "Decision Quality",
        Parameter = paste0("Residuals (N = ", length(residuals(exp2_dist_lm)), ")"),
        `Sum Sq` = sum(residuals(exp2_dist_lm)^2) |> round_to_three(),
        NumDF = NA,
        DenDF = NA,
        `Mean Sq` = (sum(residuals(exp2_dist_lm)^2)/
                       length(residuals(exp2_dist_lm))) |> round_to_three(),
        `F Value` = NA,
        p.value = NA,
        Eta2_partial = NA
        )) |>
      rbind(c(DV = "Decision Change",
        Parameter = paste0("Residuals (N = ", length(residuals(exp2_movt_lm)), ")"),
        `Sum Sq` = sum(residuals(exp2_movt_lm)^2) |> round_to_three(),
        NumDF = NA,
        DenDF = NA,
        `Mean Sq` = (sum(residuals(exp2_movt_lm)^2)/
                       length(residuals(exp2_movt_lm))) |> round_to_three(),
        `F Value` = NA,
        p.value = NA,
        Eta2_partial = NA
        )) |>
      rbind(c(DV = "Trust",
        Parameter = paste0("Residuals (N = ", length(residuals(exp2_trust_lm)), ")"),
        `Sum Sq` = sum(residuals(exp2_trust_lm)^2) |> round_to_three(),
        NumDF = NA,
        DenDF = NA,
        `Mean Sq` = (sum(residuals(exp2_trust_lm)^2)/
                       length(residuals(exp2_trust_lm))) |> round_to_three(),
        `F Value` = NA,
        p.value = NA,
        Eta2_partial = NA
        )) |>
  gt() |>
  gtsave(here("tbl_Exp2_ANOVA.docx"))

### Experiment 2 Decision Confidence Table
anova(exp2_confidence_lm) |>
        rename(p.value = `Pr(>F)`) |>
        cbind(effectsize::eta_squared(exp2_confidence_lm, partial = TRUE)) |>
        mutate(DV = "Decision Conflict",
               stars = gtools::stars.pval(p.value)) |>
  mutate_if(is.numeric, round_to_three) |>
  mutate(p.value = paste(p.value, stars)) |>
  select(DV, Parameter, `Sum Sq`, NumDF, DenDF, `Mean Sq`,
         `F value`, p.value, Eta2_partial) |>
  rbind(c(DV = "Decision Conflict",
        Parameter = paste0("Residuals (N = ", length(residuals(exp2_confidence_lm)), ")"),
        `Sum Sq` = sum(residuals(exp2_confidence_lm)^2) |> round_to_three(),
        NumDF = NA,
        DenDF = NA,
        `Mean Sq` = (sum(residuals(exp2_confidence_lm)^2)/
                       length(residuals(exp2_confidence_lm))) |> round_to_three(),
        `F Value` = NA,
        p.value = NA,
        Eta2_partial = NA
        )) |>
  gt() |>
  gtsave(here::here("tbl_Exp2_confidence_ANOVA.docx"))

### Experiment 2 WoA Table
anova(exp2_WoA_lm) |>
        rename(p.value = `Pr(>F)`) |>
        cbind(effectsize::eta_squared(exp2_WoA_lm, partial = TRUE)) |>
        mutate(DV = "WeightOnAdvice",
               stars = gtools::stars.pval(p.value)) |>
  mutate_if(is.numeric, round_to_three) |>
  mutate(p.value = paste(p.value, stars)) |>
  select(DV, Parameter, `Sum Sq`, NumDF, DenDF, `Mean Sq`,
         `F value`, p.value, Eta2_partial) |>
  rbind(c(DV = "WeightOnAdvice",
        Parameter = paste0("Residuals (N = ", length(residuals(exp2_WoA_lm)), ")"),
        `Sum Sq` = sum(residuals(exp2_WoA_lm)^2) |> round_to_three(),
        NumDF = NA,
        DenDF = NA,
        `Mean Sq` = (sum(residuals(exp2_WoA_lm)^2)/
                       length(residuals(exp2_WoA_lm))) |> round_to_three(),
        `F Value` = NA,
        p.value = NA,
        Eta2_partial = NA
        )) |>
  gt() |>
  gtsave(here::here("tbl_Exp2_WoA_ANOVA.docx"))

```

#### Exp2 Pairwise Comparisons

```{r}
#Pairwise comparisons of trust
aov(EmotionalTrust ~ Role * Quality,
    data = exp2_data) |> TukeyHSD()

exp2_data |> group_by(Quality, Role) |> summarize(mean_trust = mean(EmotionalTrust))
```

### Exp2 Figure

```{r}
### AI Influence
fig_exp2_AIinfluence <- exp2_data |>
  group_by(Quality, Explanation) |>
  summarize(n = n(),
            mean = mean(AbsMovement, na.rm = TRUE),
            se = sd(AbsMovement, na.rm = TRUE)/sqrt(n)) |>
  ggplot(aes(x = Quality,
             y = mean,
             color = Explanation,
             ymin = mean - 1.96 * se,
             ymax = mean + 1.96 * se)) +
    geom_hline(aes(yintercept = 0), color = "#D6D4CD") +
    geom_pointrange(position = position_dodge(0.4)) +
    scale_color_manual(values = c("darkblue","#228833"),
                       labels = c("Global", "Global +\nWhat")) +
    labs(y = "AI Influence\n(mg)",
         x = "AI Recommendation Quality",
         color = "AI Explanation") +
    ylim(0,1.5) +
    theme_jdc() +
    theme(axis.title.y = element_text(angle = 0),
          axis.ticks.y = element_blank(),
          legend.position = "right")

ggsave(here::here("fig_exp2_AIinfluence.png"), fig_exp2_AIinfluence, width = 5, height = 3)

### Decision Quality
fig_exp2_decision_quality <- exp2_data |>
  group_by(Quality, Role) |>
  summarize(n = n(),
            mean = mean(DistanceFinal, na.rm = TRUE),
            se = sd(DistanceFinal, na.rm = TRUE)/sqrt(n)) |>
  mutate(Quality = factor(Quality,
                          levels = c("Low", "NA", "High"))) |>
  ggplot(aes(x = Role,
             y = mean,
             color = Quality,
             ymin = mean - 1.96 * se,
             ymax = mean + 1.96 * se)) +
    geom_hline(aes(yintercept = 0), color = "#D6D4CD") +
    geom_pointrange(position = position_dodge(0.4)) +
    scale_color_manual(values = c("Low" = "darkblue",
                                  "High" = "#228833")) +
  scale_x_discrete(labels = c("Other" = "Midlevel\nor Nurse", "Pharmacist" = "Pharmacist", "Physician" = "Physician")) +
    labs(y = "Distance (mg)\nfrom Correct Dose\n(Lower is better)",
         x = "Clinical Role",
         color = "AI Quality",
         subtitle = "Panel A: Final Decision Quality") +
    ylim(0,5) +
    theme_jdc() +
    theme(axis.title.y = element_text(angle = 0),
          axis.ticks.y = element_blank())

### Emotional Trust
fig_exp2_trust <- exp2_data |>
  group_by(Quality, Role) |>
  summarize(n = n(),
            mean = mean(EmotionalTrust, na.rm = TRUE),
            se = sd(EmotionalTrust, na.rm = TRUE)/sqrt(n)) |>
  mutate(Quality = factor(Quality,
                          levels = c("Low", "NA", "High"))) |>
  ggplot(aes(x = Role,
             y = mean,
             color = Quality,
             ymin = mean - 1.96 * se,
             ymax = mean + 1.96 * se)) +
    geom_hline(aes(yintercept = 1), color = "#D6D4CD") +
    geom_hline(aes(yintercept = 5), color = "#D6D4CD") +
    geom_pointrange(position = position_dodge(0.4)) +
    scale_color_manual(values = c("Low" = "darkblue",
                                  "High" = "#228833")) +
  scale_x_discrete(labels = c("Other" = "Midlevel\nor Nurse", "Pharmacist" = "Pharmacist", "Physician" = "Physician")) +
    labs(y = "Trust",
         x = "Clinical Role",
         color = "AI Quality",
         subtitle = "Panel B: Trust") +
    ylim(1,5) +
    theme_jdc() +
    theme(axis.title.y = element_text(angle = 0),
          axis.ticks.y = element_blank())





### WeightOfAdvice by Role
fig_exp2_WoA_by_role <- exp2_data |>
  filter(!Outlier) |>
  group_by(Quality, Role) |>
  summarize(n = n(),
            mean = mean(WeightOnAdvice, na.rm = TRUE),
            se = sd(WeightOnAdvice, na.rm = TRUE)/sqrt(n)) |>
  mutate(Role = if_else(Role == "Other", "Midlevel\nor Nurse", Role)) |>
  ggplot(aes(x = Role,
             y = mean,
             color = Quality,
             ymin = mean - 1.96 * se,
             ymax = mean + 1.96 * se)) +
    geom_hline(aes(yintercept = 0), color = "#D6D4CD") +
    geom_hline(aes(yintercept = 1), color = "#D6D4CD") +
    geom_pointrange(position = position_dodge(0.4)) +
    scale_color_manual(values = c("Low" = "darkblue",
                                  "High" = "#228833")) +
    scale_y_continuous(breaks = seq(0, 1, 0.25),
                       labels = scales::percent_format(accuracy = 1),
                       limits = c(-0.05, 1)) +
    labs(y = "Weight\nof\nAdvice",
         x = "Clinical Role",
         color = "AI Quality",
         subtitle = "Panel C: AI Influence") +
    theme_jdc() +
    theme(axis.title.y = element_text(angle = 0),
          axis.ticks.y = element_blank(),
          legend.position = "bottom")

# Save the figure
ggsave(here::here("fig_exp2_WoA_Supplement.png"), fig_exp2_WoA_by_role, width = 4, height = 3)

### WoA
fig_exp2_WoA <- exp2_data |>
  filter(!Outlier & !is.na(WeightOnAdvice) & !is.infinite(WeightOnAdvice)) |>
  group_by(Quality, Explanation) |>
  summarize(n = n(),
            mean = mean(WeightOnAdvice, na.rm = TRUE),
            se = sd(WeightOnAdvice, na.rm = TRUE)/sqrt(n)) |>
  ggplot(aes(x = Quality,
             y = mean,
             color = Explanation,
             ymin = mean - 1.96 * se,
             ymax = mean + 1.96 * se)) +
    geom_hline(aes(yintercept = 0), color = "#D6D4CD") +
    geom_pointrange(position = position_dodge(0.5)) +
    scale_color_manual(values = theme_paultol_colors(4)) +
    labs(y = "Weight\nof\nAdvice",
         x = "AI Recommendation Quality",
         color = "AI Explanation") +
    scale_y_continuous(breaks = seq(0, 1, 0.25),
                       labels = scales::percent_format(accuracy = 1),
                       limits = c(0, 1)) +
    theme_jdc() +
    theme(axis.title.y = element_text(angle = 0),
          axis.ticks.y = element_blank(),
          legend.position = "right")

# Save the figure
ggsave(here::here("fig_exp2_WoA.png"), fig_exp2_WoA,
       width = 6, height = 3)

### Combine the figures with the patchwork package
exp2_figure <- fig_exp2_decision_quality + fig_exp2_trust + fig_exp2_WoA_by_role + 
  plot_layout(ncol = 3) +
  plot_layout(guides = "collect") & theme(legend.position = 'bottom')

# Save the figure
ggsave(here::here("fig_exp2.png"), exp2_figure, width = 9, height = 4)

```

Exp2 Pairwise Comparisons

```{r}
# Influence
exp2_data |>
  group_by(Explanation, Quality) |>
  summarize(mean(AbsMovement))

aov(AbsMovement ~ Explanation * Quality, data = exp2_data) |> TukeyHSD()

# Decision Quality
exp2_data |>
  group_by(Role, Quality) |>
  summarize(mean(DistanceFinal))

aov(DistanceFinal ~ Quality * Role, exp2_data) |> TukeyHSD()
```

### Exp2 Trust Alpha/Corr

```{r}
psych::alpha(exp2_data |>
               select(EmotionalTrust1, EmotionalTrust2, EmotionalTrust3))$total$raw_alpha

corr_exp2 <- corr.test(exp2_data |>
            filter(!is.na(EmotionalTrust)) |>
            select(EmotionalTrust, DistanceFinal))

corr_exp2_high <- corr.test(exp2_data |>
            filter(!is.na(EmotionalTrust) & Quality == "High") |>
            select(EmotionalTrust, DistanceFinal))

corr_exp2_low <- corr.test(exp2_data |>
            filter(!is.na(EmotionalTrust) & Quality == "Low") |>
            select(EmotionalTrust, DistanceFinal))

print(paste0("Overall r(",corr_exp2$n-2,") = ",
             round(corr_exp2$r[1,2], 2),
             ", p=",
             round(corr_exp2$p[1,2], 4)))

print(paste0("High Quality r(",corr_exp2_high$n-2,") = ",
             round(corr_exp2_high$r[1,2], 2),
             ", p=",
             round(corr_exp2_high$p[1,2], 4)))

print(paste0("Low Quality r(",corr_exp2_low$n-2,") = ",
             round(corr_exp2_low$r[1,2], 2),
             ", p=",
             round(corr_exp2_low$p[1,2], 4)))
```

## Experiment 3

### Exp 3 Manipulation Checks

```{r ManipCheck, echo=FALSE, message=FALSE, warning=FALSE}
### Manipulation Checks
exp3_ManipCheck_df <- exp3_data |> 
  group_by(ResponseId) |>
  filter(row_number() == 1)

exp3_ManipChk_aov_What <- aov(ManipCheck_What ~ Exp_What, data = exp3_ManipCheck_df)
exp3_ManipChk_aov_Why <- aov(ManipCheck_Why ~ Exp_Why, data = exp3_ManipCheck_df)
exp3_ManipChk_aov_How <- aov(ManipCheck_How ~ Exp_How, data = exp3_ManipCheck_df)

exp3_ManipChk_pvals <- tibble(f = c(1, 2, 3),
                         p = c(summary(exp3_ManipChk_aov_What)[[1]][["Pr(>F)"]][1],
                               summary(exp3_ManipChk_aov_Why)[[1]][["Pr(>F)"]][1],
                               summary(exp3_ManipChk_aov_How)[[1]][["Pr(>F)"]][1]),
                         x = c(1, 2, 3),
                         y = rep(1.8, each = 3)) |>
  mutate(p = case_when(p >= 0.001 ~ paste0("p = ", round(p, 3)),
                       p < 0.001 ~ "p < 0.001"))

### Tukey HSD
aov(ManipCheck_What ~ ExpPower, data = exp3_ManipCheck_df) |> TukeyHSD()
aov(ManipCheck_Why ~ ExpPower, data = exp3_ManipCheck_df) |> TukeyHSD()

### Plot Manip Check
exp3_ManipCheck_df <- exp3_ManipCheck_df |>
  select(ExpPower, contains("ManipCheck")) |> 
  pivot_longer(cols = contains("ManipCheck"),
               names_to = "ManipCheck",
               values_to = "Response")

pd <- position_dodge(width = 0.4)
gray_boxes <- tibble(f = rep(1:3, times = 1, each = 4),
                     x = rep(c(0.875, 1.25, 2, 2.25, 3.125, 3.25), times = 1, each = 2),
                     y = c(3.2,     4.7,    4.7,   3.2,
                           3.5,     4.5,    4.5,   3.5,
                           3.5,     4.5,    4.5,   3.5))

# Make plot
ManipChkPlot <- exp3_ManipCheck_df |>
  group_by(ManipCheck, ExpPower) |>
  summarise(TotalResponse = mean(Response, na.rm = TRUE),
            se = sd(Response, na.rm = TRUE)/sqrt(n())) |>
  mutate(ManipCheck = factor(ManipCheck, levels = c("ManipCheck_What",
                                                     "ManipCheck_Why",
                                                     "ManipCheck_How"))) |>
  ggplot(aes(x = ManipCheck, group = ExpPower)) +
  geom_hline(aes(yintercept = 1), color = "#D6D4CD") +
  geom_hline(aes(yintercept = 5), color = "#D6D4CD") +
  geom_polygon(data = gray_boxes, aes(x = x, y = y, group = f), fill = "gray90") +
  geom_pointrange(aes(y = TotalResponse,
                      ymin = TotalResponse - 1.96 * se,
                      ymax = TotalResponse + 1.96 * se,
                      color = ExpPower),
                  position = position_dodge(0.5)) +
  geom_text(data = exp3_ManipChk_pvals, aes(x = x, y = y, label = p, group = f)) +
  labs(y = "Response",
       x = "Manipulation Check Question",
       color = "AI Explanation Condition",
       subtitle = "Conditions in the gray boxes included the relevant information and\nshould read higher than those outside if the manipulation worked",
       caption = "P-values reported from ANOVA comparing conditions where\ninformation was given to those where it was not.") +
  ylim(1,5) +
  scale_x_discrete(labels = c("ManipCheck_How" = "HOW\nRelative importance ...",
                              "ManipCheck_What" = "WHAT\nWhich factors ...",
                              "ManipCheck_Why" = "WHY\nWhy factors ...")) +
  scale_color_manual(values = theme_paultol_colors(4)) +
  theme_jdc()

# Output plot
ggsave(plot = ManipChkPlot, filename = here::here("fig_exp3_manip_check.png"),
       height = 4, width = 5.5)


### Manipulation Checks REVISED
exp3_ManipCheck_df <- exp3_data |> 
  group_by(ResponseId) |>
  filter(row_number() == 1)

exp3_ManipChk_aov_What <- aov(ManipCheck_What ~ Exp_What, data = exp3_ManipCheck_df)
exp3_ManipChk_aov_Why <- aov(ManipCheck_Why ~ Exp_Why, data = exp3_ManipCheck_df)
exp3_ManipChk_aov_How <- aov(ManipCheck_How ~ Exp_How, data = exp3_ManipCheck_df)

exp3_ManipChk_pvals <- tibble(f = c(1, 2, 3),
                         p = c(summary(exp3_ManipChk_aov_What)[[1]][["Pr(>F)"]][1],
                               summary(exp3_ManipChk_aov_Why)[[1]][["Pr(>F)"]][1],
                               summary(exp3_ManipChk_aov_How)[[1]][["Pr(>F)"]][1]),
                         x = c(1, 2, 3),
                         y = rep(1.8, each = 3)) |>
  mutate(p = case_when(p >= 0.001 ~ paste0("p = ", round(p, 3)),
                       p < 0.001 ~ "p < 0.001"))

### Tukey HSD
aov(ManipCheck_What ~ ExpPower, data = exp3_ManipCheck_df) |> TukeyHSD()
aov(ManipCheck_Why ~ ExpPower, data = exp3_ManipCheck_df) |> TukeyHSD()

### Plot Manip Check
exp3_ManipCheck_df <- exp3_ManipCheck_df |>
  select(ExpPower, contains("ManipCheck")) |> 
  pivot_longer(cols = contains("ManipCheck"),
               names_to = "ManipCheck",
               values_to = "Response")

pd <- position_dodge(width = 0.4)
gray_boxes <- tibble(f = rep(1:3, times = 1, each = 4),
                     x = rep(c(0.875, 1.25, 2, 2.25, 3.125, 3.25), times = 1, each = 2),
                     y = c(3.2,     4.7,    4.7,   3.2,
                           3.5,     4.5,    4.5,   3.5,
                           3.5,     4.5,    4.5,   3.5))

# Make plot
ManipChkPlot2 <- exp3_ManipCheck_df |>
  group_by(ManipCheck, ExpPower) |>
  summarise(TotalResponse = mean(Response, na.rm = TRUE),
            se = sd(Response, na.rm = TRUE)/sqrt(n())) |>
  mutate(
         ManipCheck = factor(ManipCheck, levels = c("ManipCheck_What",
                                                     "ManipCheck_Why",
                                                     "ManipCheck_How"))) |>
  ggplot(aes(x = ExpPower, group = ManipCheck)) +
  geom_hline(aes(yintercept = 1), color = "#D6D4CD") +
  geom_hline(aes(yintercept = 5), color = "#D6D4CD") +
  geom_pointrange(aes(y = TotalResponse,
                      ymin = TotalResponse - 1.96 * se,
                      ymax = TotalResponse + 1.96 * se,
                      color = ManipCheck),
                  position = position_dodge(0.5)) +
  labs(y = "Response",
       x = "AI Explanation Condition",
       color = "Manipulation Check Question") +
  ylim(1,5) +
  scale_x_discrete(labels = c("1" = "Global\nExplanation...",
                              "2" = "+ Local \nWhat...",
                              "3" = "+ What...",
                              "4" = "+ How")) +
  scale_color_manual(values = theme_paultol_colors(3),
                     labels = c("What", "Why", "How")) +
  theme_jdc()

# Output plot
ggsave(plot = ManipChkPlot2, filename = here::here("fig_exp3_manip_check_altversion.png"),
       height = 4, width = 5.5)
```

### Exp3 Initial Judgment by Role

```{r}
### Initial Judgment by Role
fig_exp3_initaljudgments <- exp3_data |>
  group_by(Role) |>
  summarize(n = n(),
            mean = mean(DistanceInitial, na.rm = TRUE),
            se = sd(DistanceInitial, na.rm = TRUE)/sqrt(n)) |>
  ggplot(aes(x = Role,
             y = mean,
             ymin = mean - 1.96 * se,
             ymax = mean + 1.96 * se)) +
    geom_pointrange(position = position_dodge(0.4),
                    color = theme_paultol_colors(1)) +
    labs(y = "Distance (mg)\nfrom Correct Dose\n(Lower is better)",
         x = "",
         title = "Initial Decision Quality (before viewing AI)") +
    theme_jdc() +
    theme(axis.title.y = element_text(angle = 0),
          axis.ticks.y = element_blank())

# Save the figure
ggsave(here::here("fig_exp3_initaljudgments.png"), fig_exp3_initaljudgments,
       width = 6, height = 3)

aov(lm(DistanceInitial ~ Role, data = exp3_data)) |> TukeyHSD()
aov(lm(DistanceInitial ~ Qualifications, data = exp3_data)) |> TukeyHSD()

```

### Exp3 Qual Movements

```{r}
### Summarize by median
exp3_qual_table <- exp3_data |>
  filter(!Outlier) |>
  group_by(Scenario, Quality) |>
  summarize(n = n(),
            Changed = sum(AbsMovement > 0),
            PctChange = scales::percent(Changed/n, accuracy = 0.1),
            Improved = sum(Improvement > 0),
            PctImproved = scales::percent(Improved/n, accuracy = 0.1)
            ) |>
  ungroup() |>
  rename(`No. Obs.` = n) |>
  mutate(`Changed (%)` = paste0(Changed, " (", PctChange, ")"),
         `Improved (%)` = paste0(Improved, " (", PctImproved, ")")
  ) |>
  select(-Changed, -PctChange, -Improved, -PctImproved) |>
  flextable::regulartable() |>
  flextable::autofit()

### Export the Table to a Word Doc for Pasting
word_document_name <-
    officer::read_docx() |>
    flextable::body_add_flextable(exp3_qual_table) |>
    print(target = here::here("tab_exp3_qualtable.docx"))
```

### Exp3 Individual Movements

```{r}
movt_df <- exp3_data |>
  group_by(Scenario, Quality, Explanation) |>
  filter(InitialDose <= 12 & !Outlier) |>
  arrange(InitialDose, Movement, .by_group = TRUE) |>
  mutate(CorrectDose = if_else(CorrectDose == 5.5,
                                 "Scenario 1, Correct Dose 5.5mg",
                                 "Scenario 2, Correct Dose 9mg"),
         Quality = if_else(Quality == "Low", "Low Quality Rec", "High Quality Rec")
  )


movt_df$rowID = as.numeric(rownames(movt_df))

movt_df <- movt_df |>
  ungroup() |>
  group_by(CorrectDose, Quality) %>%
  mutate(rowID = rowID - min(rowID)) |>
  ungroup()

movt_df_labels <- tribble(
  ~text,         ~Quality,             ~CorrectDose,                        ~x,    ~y, ~label_hjust,
  "AI Recc",     "Low Quality Rec",    "Scenario 1, Correct Dose 5.5mg",  12, 3, 1,
  "AI Recc",     "Low Quality Rec",    "Scenario 2, Correct Dose 9mg",    12.8,    3, 1,
  "Patient's\nPrior\nDose", "High Quality Rec","Scenario 1, Correct Dose 5.5mg",7.7,80, 0,
  "Patient's\nPrior\nDose", "High Quality Rec","Scenario 2, Correct Dose 9mg",11.2,80,0
  )

ggplot() +
  geom_vline(data = movt_df,
             aes(xintercept = if_else(CorrectDose == "Scenario 1, Correct Dose 5.5mg",
                                      5.5, 9)),
             color = "gray40") +
  geom_vline(data = movt_df,
             aes(xintercept = AIDose), color = "gray40", linetype = 2) +
  geom_vline(data = movt_df,
             aes(xintercept = StartingDose), color = "gray40", linetype = 3) +
  geom_point(data = movt_df,
             aes(x = InitialDose,
                 y = rowID,
                 color = Explanation),
             size = 1) +
  geom_point(data = movt_df |> filter(InitialDose != FinalDose),
             aes(x = FinalDose,
                 y = rowID,
                 color = Explanation),
             size = 2) +
  geom_segment(data = movt_df %>%
                 filter(InitialDose - FinalDose > 0),
               aes(x = InitialDose, xend = FinalDose+0.1,
                   y = rowID, yend = rowID),
               arrow = arrow(length = unit(0.02, "npc")),
               color = "gray20") +
  geom_segment(data = movt_df %>%
                 filter(InitialDose - FinalDose < 0),
               aes(x = InitialDose, xend = FinalDose-0.1,
                   y = rowID, yend = rowID),
               arrow = arrow(length = unit(0.02, "npc")),
               color = "gray20") +
  geom_text(data = movt_df_labels, aes(x = x, y = y, label = text),
            color = "gray20", hjust = movt_df_labels$label_hjust) +
  labs(title = "Individual Decision Adjustment Plot",
       y = "",
       x = "Dose Selected (mg)",
       color = "Explanation Condition") +
  scale_color_manual(values = theme_paultol_colors(4)) +
  scale_x_continuous(breaks = seq(0, 12, 2)) +
  theme_jdc() +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5),
        axis.text.y = element_blank(),
        axis.text.x = element_text(size = 12),
        axis.ticks.y = element_blank(),
        plot.title = element_text(size = 16),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12)) +
  facet_grid(Quality ~ CorrectDose, scales = "free_x")
```

### Exp3 ANOVA

```{r}
### Run Linear Regressions to then conduct ANOVA
# Final Decision Quality
exp3_dist_lm <- lmer(DistanceFinal ~ Explanation + Quality + Role +
        Explanation:Quality + Explanation:Role + Quality:Role + (1|ResponseId), 
        data = exp3_data)

print("Decision Quality (Final Distance in mg)")
anova(exp3_dist_lm)

# AI Influence measured as Absolute Movement
exp3_movt_lm <- lmer(AbsMovement ~ Explanation + Quality + Role +
        Explanation:Quality + Explanation:Role + Quality:Role + (1|ResponseId), 
        data = exp3_data)

print("Absolute Movement (Distance in mg)")
anova(exp3_movt_lm)

# Trust
exp3_trust_lm <- lmer(EmotionalTrust ~ Explanation + Quality + Role +
        Explanation:Quality + Explanation:Role + Quality:Role + (1|ResponseId), 
        data = exp3_data)

# Improvement
exp3_improvement_lm <- lmer(Improvement ~ Explanation + Quality + Role + Scenario +
      Explanation:Quality +  Explanation:Role + Explanation:Scenario +
        Quality:Role + Quality:Scenario + Role:Scenario + (1|ResponseId), 
        data = exp3_data)

print("Improvement")
anova(exp3_improvement_lm)

# Decision Conflict
exp3_conflict_lm <- lmer(DecisionConflict ~ Explanation + Quality + Role +
      Explanation:Quality +  Explanation:Role +
        Quality:Role + (1|ResponseId), 
        data = exp3_data)
anova(exp3_conflict_lm)

# Quality with Emotional Trust as a Moderator
exp3_dist_trust_lm <- lmer(DistanceFinal ~ Explanation + Quality + Role + EmotionalTrust
+        Explanation:Quality + Explanation:Role + Quality:Role + EmotionalTrust:Quality + EmotionalTrust:Role + (1|ResponseId), 
        data = exp3_data)

print("Decision Quality (Final Distance in mg) w/ Trust as Moderator")
anova(exp3_dist_trust_lm)

### Add Scenario
# AI Influence
exp3_scenario_movt_lm <- lm(AbsMovement ~ Explanation + Quality + Role + Scenario +
      Explanation:Quality +  Explanation:Role + Explanation:Scenario +
        Quality:Role + Quality:Scenario + Role:Scenario, 
        data = exp3_data)

# Decision Quality
exp3_scenario_dist_lm <- lm(DistanceFinal ~ Explanation + Quality + Role + Scenario +
      Explanation:Quality +  Explanation:Role + Explanation:Scenario +
        Quality:Role + Quality:Scenario + Role:Scenario, 
        data = exp3_data)


# By Role
aov(DistanceFinal ~ Role, data = exp3_data) |> TukeyHSD()

exp3_data |>
  group_by(Role) |>
  summarize(mean_DistanceFinal = mean(DistanceFinal))

### ANALYSES ADDED FOR REVIEW
# Weight On Advice
exp3_WoA_lm <- lmer(WeightOnAdvice ~ Explanation + Quality + Role +
        Explanation:Quality + Explanation:Role + Quality:Role + (1|ResponseId), 
        data = exp3_data)

anova(exp3_WoA_lm)

# Pairwise Comparisons
aov(WeightOnAdvice ~ Role * Quality, data = exp3_data) |> TukeyHSD()
aov(WeightOnAdvice ~ Explanation * Quality, data = exp3_data) |> TukeyHSD()

# Difference in WoA between low and high quality.
exp3_data |>
  group_by(Quality) |>
  summarize(mean_WoA = mean(WeightOnAdvice, na.rm = TRUE))

# Power analysis for WoA Explanation/Quality
emm <- emmeans(exp3_WoA_lm, ~ Explanation * Quality)
pairs_df <- as.data.frame(pairs(emm, adjust = "tukey"))
sigma_model <- sigma(exp3_WoA_lm) # Residual SD from the model
n_per_cell  <- mean(table(exp3_data$Quality, exp3_data$Explanation)[2:3,])
alpha_adj   <- 0.05 / nrow(pairs_df)

pairs_df$cohens_d <- pairs_df$estimate / sigma_model

pairs_df$power <- mapply(function(d, se) {
  pwr.t.test(n = n_per_cell, d = abs(d),
             sig.level = alpha_adj, type = "two.sample")$power
}, pairs_df$cohens_d, pairs_df$SE)

pairs_df$n_needed <- sapply(pairs_df$cohens_d, function(d) {
  ceiling(pwr.t.test(d = abs(d), sig.level = alpha_adj,
                     power = 0.80, type = "two.sample")$n)
})
pairs_df # Show the results; n_needed is *per cell*


# Final Decision Quality w/ add'l controls
exp3_dist_w_controls_lm <- lmer(DistanceFinal ~ Explanation + Quality + Role +
        Explanation:Quality + Explanation:Role + Quality:Role + Age + Gender + YearsExperience + (1|ResponseId), 
        data = exp3_data)

print("Decision Quality (Final Distance in mg) w/ controls")
anova(exp3_dist_w_controls_lm)

# Individual Trust Items
exp3_trust1_lm <- lmer(EmotionalTrust_1 ~ Explanation + Quality + Role +
+        Explanation:Quality + Explanation:Role + Quality:Role + (1|ResponseId), 
        data = exp3_data)
exp3_trust2_lm <- lmer(EmotionalTrust_2 ~ Explanation + Quality + Role +
+        Explanation:Quality + Explanation:Role + Quality:Role + (1|ResponseId), 
        data = exp3_data)
exp3_trust3_lm <- lmer(EmotionalTrust_3 ~ Explanation + Quality + Role +
+        Explanation:Quality + Explanation:Role + Quality:Role + (1|ResponseId), 
        data = exp3_data)

anova(exp3_trust1_lm)
anova(exp3_trust2_lm)
anova(exp3_trust3_lm)

# Correlation Table Among Trust Items and Decision Quality
cor(exp3_data |> 
        select(DistanceFinal, EmotionalTrust_1,
               EmotionalTrust_2, EmotionalTrust_3),
    use = "pairwise.complete.obs") |>
  as.data.frame() |>
  round_to_three() |>
  gt() |>
  gtsave(here("tbl_Exp3_TRUST_QUALITY_TABLE.docx"))

```

#### Exp3 ANOVA Tables

```{r}
### ANOVA Table formatting in APA style
rbind(anova(exp3_dist_lm) |>
        rename(p.value = `Pr(>F)`) |>
        cbind(effectsize::eta_squared(exp3_dist_lm, partial = TRUE)) |>
        mutate(DV = "Decision Quality",
               stars = gtools::stars.pval(p.value)),
      anova(exp3_movt_lm) |>
        rename(p.value = `Pr(>F)`) |>
        cbind(effectsize::eta_squared(exp3_movt_lm, partial = TRUE)) |>
        mutate(DV = "Influence",
               stars = gtools::stars.pval(p.value))
      ) |>
  mutate_if(is.numeric, round_to_three) |>
  mutate(p.value = paste(p.value, stars)) |>
  select(DV, Parameter, `Sum Sq`, NumDF, DenDF, `Mean Sq`,
         `F value`, p.value, Eta2_partial) |>
    rbind(c(DV = "Decision Quality",
        Parameter = paste0("Residuals (N = ", length(residuals(exp3_dist_lm)), ")"),
        `Sum Sq` = sum(residuals(exp3_dist_lm)^2) |> round_to_three(),
        NumDF = NA,
        DenDF = NA,
        `Mean Sq` = (sum(residuals(exp3_dist_lm)^2)/
                       length(residuals(exp3_dist_lm))) |> round_to_three(),
        `F Value` = NA,
        p.value = NA,
        Eta2_partial = NA
        )) |>
      rbind(c(DV = "Influence",
        Parameter = paste0("Residuals (N = ", length(residuals(exp3_movt_lm)), ")"),
        `Sum Sq` = sum(residuals(exp3_movt_lm)^2) |> round_to_three(),
        NumDF = NA,
        DenDF = NA,
        `Mean Sq` = (sum(residuals(exp3_movt_lm)^2)/
                       length(residuals(exp3_movt_lm))) |> round_to_three(),
        `F Value` = NA,
        p.value = NA,
        Eta2_partial = NA
        )) |>
  gt() |>
  gtsave(here("tbl_Exp3_ANOVA.docx"))

### Experiment 3 Trust Table
rbind(anova(exp3_trust_lm) |>
        rename(p.value = `Pr(>F)`) |>
        cbind(effectsize::eta_squared(exp3_trust_lm, partial = TRUE)) |>
        mutate(DV = "Emotional Trust",
               stars = gtools::stars.pval(p.value))
      ) |>
  mutate_if(is.numeric, round_to_three) |>
  mutate(p.value = paste(p.value, stars)) |>
  select(DV, Parameter, `Sum Sq`, NumDF, DenDF, `Mean Sq`,
         `F value`, p.value, Eta2_partial) |>
  
      rbind(c(DV = "Trust",
        Parameter = paste0("Residuals (N = ", length(residuals(exp3_trust_lm)), ")"),
        `Sum Sq` = sum(residuals(exp3_trust_lm)^2) |> round_to_three(),
        NumDF = NA,
        DenDF = NA,
        `Mean Sq` = (sum(residuals(exp3_trust_lm)^2)/
                       length(residuals(exp3_trust_lm))) |> round_to_three(),
        `F Value` = NA,
        p.value = NA,
        Eta2_partial = NA
        )) |>
  gt() |>
  gtsave(here::here("tbl_Exp3_trust_ANOVA.docx"))

### Experiment 3 WoA Table
anova(exp3_WoA_lm) |>
        rename(p.value = `Pr(>F)`) |>
        cbind(effectsize::eta_squared(exp3_WoA_lm, partial = TRUE)) |>
        mutate(DV = "WeightOnAdvice",
               stars = gtools::stars.pval(p.value)) |>
  mutate_if(is.numeric, round_to_three) |>
  mutate(p.value = paste(p.value, stars)) |>
  select(DV, Parameter, `Sum Sq`, NumDF, DenDF, `Mean Sq`,
         `F value`, p.value, Eta2_partial) |>
  rbind(c(DV = "WeightOnAdvice",
        Parameter = paste0("Residuals (N = ", length(residuals(exp3_WoA_lm)), ")"),
        `Sum Sq` = sum(residuals(exp3_WoA_lm)^2) |> round_to_three(),
        NumDF = NA,
        DenDF = NA,
        `Mean Sq` = (sum(residuals(exp3_WoA_lm)^2)/
                       length(residuals(exp3_WoA_lm))) |> round_to_three(),
        `F Value` = NA,
        p.value = NA,
        Eta2_partial = NA
        )) |>
  gt() |>
  gtsave(here::here("tbl_Exp3_WoA_ANOVA.docx"))

### Improvement Table for Appendix
anova(exp3_improvement_lm) |>
        rename(p.value = `Pr(>F)`) |>
        cbind(effectsize::eta_squared(exp3_improvement_lm, partial = TRUE)) |>
        mutate(DV = "Improvement",
               stars = gtools::stars.pval(p.value)) |>
  mutate_if(is.numeric, round_to_three) |>
  mutate(p.value = paste(p.value, stars)) |>
  select(DV, Parameter, `Sum Sq`, NumDF, DenDF, `Mean Sq`,
         `F value`, p.value, Eta2_partial)  |>
  rbind(c(DV = "Improvement",
        Parameter = paste0("Residuals (N = ", length(residuals(exp3_improvement_lm)), ")"),
        `Sum Sq` = sum(residuals(exp3_improvement_lm)^2) |> round_to_three(),
        NumDF = NA,
        DenDF = NA,
        `Mean Sq` = (sum(residuals(exp3_improvement_lm)^2)/
                       length(residuals(exp3_improvement_lm))) |> round_to_three(),
        `F Value` = NA,
        p.value = NA,
        Eta2_partial = NA
        )) |>
  gt() |>
  gtsave(here::here("tbl_Exp3_improvement_ANOVA.docx"))

### Scenario Table for Appendix
rbind(sjstats::anova_stats(car::Anova(exp3_scenario_movt_lm, type = 3)) |>
        mutate(DV = "Influence",
               stars = gtools::stars.pval(p.value)),
      sjstats::anova_stats(car::Anova(exp3_scenario_dist_lm, type = 3)) |>
        mutate(DV = "Decision Quality",
               stars = gtools::stars.pval(p.value))
      ) |>
  mutate_if(is.numeric, round_to_three) |>
  mutate(p.value = paste(p.value, stars)) |>
  select(DV, term, sumsq, df, meansq,
         `F stat`=statistic, p.value, partial.etasq) |>
  gt() |>
  gtsave(here::here("tbl_Exp3_Scenario_ANOVA.docx"))
```

### Exp3 Figures

```{r}
### AI Influence
fig_exp3_AIinfluence <- exp3_data |>
  group_by(Quality, Explanation) |>
  summarize(n = n(),
            mean = mean(AbsMovement, na.rm = TRUE),
            se = sd(AbsMovement, na.rm = TRUE)/sqrt(n)) |>
  ggplot(aes(x = Quality,
             y = mean,
             color = Explanation,
             ymin = mean - 1.96 * se,
             ymax = mean + 1.96 * se)) +
    geom_hline(aes(yintercept = 0), color = "#D6D4CD") +
    geom_pointrange(position = position_dodge(0.5)) +
    scale_color_manual(values = theme_paultol_colors(4)) +
    labs(y = "AI Influence\n(mg)",
         x = "AI Recommendation Quality",
         color = "AI Explanation") +
    ylim(0,2) +
    theme_jdc() +
    theme(axis.title.y = element_text(angle = 0),
          axis.ticks.y = element_blank(),
          legend.position = "right")

# Save the figure
ggsave(here::here("fig_exp3_AIinfluence.png"), fig_exp3_AIinfluence,
       width = 6, height = 3)

### WoA
fig_exp3_WoA <- exp3_data |>
  group_by(Quality, Explanation) |>
  summarize(n = n(),
            mean = mean(WeightOnAdvice, na.rm = TRUE),
            se = sd(WeightOnAdvice, na.rm = TRUE)/sqrt(n)) |>
  ggplot(aes(x = Quality,
             y = mean,
             color = Explanation,
             ymin = mean - 1.96 * se,
             ymax = mean + 1.96 * se)) +
    geom_hline(aes(yintercept = 0), color = "#D6D4CD") +
    geom_pointrange(position = position_dodge(0.5)) +
    scale_color_manual(values = theme_paultol_colors(4)) +
    labs(y = "Weight\nof\nAdvice",
         x = "AI Recommendation Quality",
         color = "AI Explanation") +
    scale_y_continuous(breaks = seq(0, 1, 0.25),
                       labels = scales::percent_format(accuracy = 1),
                       limits = c(0, 1)) +
    theme_jdc() +
    theme(axis.title.y = element_text(angle = 0),
          axis.ticks.y = element_blank(),
          legend.position = "right")

# Save the figure
ggsave(here::here("fig_exp3_WoA.png"), fig_exp3_WoA,
       width = 6, height = 3)

### AI Influence & Decision Quality by Role
fig_exp3_dist_by_role <- exp3_data |>
  group_by(Quality, Role) |>
  summarize(n = n(),
            mean = mean(DistanceFinal, na.rm = TRUE),
            se = sd(DistanceFinal, na.rm = TRUE)/sqrt(n)) |>
  mutate(Role = if_else(Role == "Other", "Midlevel\nor Nurse", Role)) |>
  ggplot(aes(x = Role,
             y = mean,
             color = Quality,
             ymin = mean - 1.96 * se,
             ymax = mean + 1.96 * se)) +
    geom_hline(aes(yintercept = 0), color = "#D6D4CD") +
    geom_pointrange(position = position_dodge(0.4)) +
    scale_color_manual(values = theme_paultol_colors(2)) +
    labs(y = "Distance (mg)\nfrom Correct Dose\n(Lower is better)",
         x = "Clinical Role",
         color = "AI Quality",
         subtitle = "Panel A: Decision Quality") +
    ylim(0,2.5) +
    theme_jdc() +
    theme(axis.title.y = element_text(angle = 0),
          axis.ticks.y = element_blank(),
          legend.position = "bottom")

fig_exp3_AIinfluence_by_role <- exp3_data |>
  group_by(Quality, Role) |>
  summarize(n = n(),
            mean = mean(AbsMovement, na.rm = TRUE),
            se = sd(AbsMovement, na.rm = TRUE)/sqrt(n)) |>
  mutate(Role = if_else(Role == "Other", "Midlevel\nor Nurse", Role)) |>
  ggplot(aes(x = Role,
             y = mean,
             color = Quality,
             ymin = mean - 1.96 * se,
             ymax = mean + 1.96 * se)) +
    geom_hline(aes(yintercept = 0), color = "#D6D4CD") +
    geom_pointrange(position = position_dodge(0.4)) +
    scale_color_manual(values = theme_paultol_colors(2)) +
    labs(y = "Decision Change\n(mg)",
         x = "Clinical Role",
         color = "AI Quality") +
    ylim(0,2.5) +
    theme_jdc() +
    theme(axis.title.y = element_text(angle = 0),
          axis.ticks.y = element_blank(),
          legend.position = "bottom")

# Save the figure
ggsave(here::here("fig_exp3_DecisionChangebyRole.png"), fig_exp3_AIinfluence_by_role,
       width = 4, height = 3)

### WeightOfAdvice by Role
fig_exp3_WoA_by_role <- exp3_data |>
  filter(!Outlier) |>
  group_by(Quality, Role) |>
  summarize(n = n(),
            mean = mean(WeightOnAdvice, na.rm = TRUE),
            se = sd(WeightOnAdvice, na.rm = TRUE)/sqrt(n)) |>
  mutate(Role = if_else(Role == "Other", "Midlevel\nor Nurse", Role)) |>
  ggplot(aes(x = Role,
             y = mean,
             color = Quality,
             ymin = mean - 1.96 * se,
             ymax = mean + 1.96 * se)) +
    geom_hline(aes(yintercept = 0), color = "#D6D4CD") +
    geom_hline(aes(yintercept = 1), color = "#D6D4CD") +
    geom_pointrange(position = position_dodge(0.4)) +
    scale_color_manual(values = theme_paultol_colors(2)) +
    scale_y_continuous(breaks = seq(0, 1, 0.25),
                       labels = scales::percent_format(accuracy = 1),
                       limits = c(0, 1)) +
    labs(y = "Weight\nof\nAdvice",
         x = "Clinical Role",
         color = "AI Quality",
         subtitle = "Panel C: AI Influence") +
    theme_jdc() +
    theme(axis.title.y = element_text(angle = 0),
          axis.ticks.y = element_blank(),
          legend.position = "bottom")

# Save the figure
ggsave(here::here("fig_exp3_WoA.png"), fig_exp3_WoA_by_role, width = 4, height = 3)

### Emotional Trust by Role
fig_exp3_Trust_by_role <- exp3_data |>
  filter(!Outlier) |>
  group_by(Quality, Role) |>
  summarize(n = n(),
            mean = mean(EmotionalTrust, na.rm = TRUE),
            se = sd(EmotionalTrust, na.rm = TRUE)/sqrt(n)) |>
  mutate(Role = if_else(Role == "Other", "Midlevel\nor Nurse", Role)) |>
  ggplot(aes(x = Role,
             y = mean,
             color = Quality,
             ymin = mean - 1.96 * se,
             ymax = mean + 1.96 * se)) +
    geom_hline(aes(yintercept = 1), color = "#D6D4CD") +
    geom_hline(aes(yintercept = 5), color = "#D6D4CD") +
    geom_pointrange(position = position_dodge(0.4)) +
    scale_color_manual(values = c("Low" = "darkblue",
                                  "High" = "#228833")) +
  scale_x_discrete(labels = c("Other" = "Midlevel\nor Nurse", "Pharmacist" = "Pharmacist", "Physician" = "Physician")) +
    labs(y = "Trust",
         x = "Clinical Role",
         color = "AI Quality",
         subtitle = "Panel B: Trust") +
    ylim(1,5) +
    theme_jdc() +
    theme(axis.title.y = element_text(angle = 0),
          axis.ticks.y = element_blank())

# Combine Plots
exp3_figure <- fig_exp3_dist_by_role + fig_exp3_Trust_by_role + fig_exp3_WoA_by_role + 
  plot_layout(ncol = 3) +
  plot_layout(guides = "collect") & theme(legend.position = 'bottom')

# Save the figure
ggsave(here::here("fig_exp3.png"), exp3_figure, width = 9, height = 4)

```

### Exp3 Emotional Trust

```{r}
# Chronbach's Alpha
psych::alpha(exp3_data |>
               filter(!is.na(EmotionalTrust)) |>
               select(EmotionalTrust_1, EmotionalTrust_2, EmotionalTrust_3))$total$raw_alpha

corr_exp3 <- corr.test(exp3_data |>
            filter(!is.na(EmotionalTrust)) |>
            select(EmotionalTrust, DistanceFinal))

corr_exp3_high <- corr.test(exp3_data |>
            filter(!is.na(EmotionalTrust) & Quality == "High") |>
            select(EmotionalTrust, DistanceFinal))

corr_exp3_low <- corr.test(exp3_data |>
            filter(!is.na(EmotionalTrust) & Quality == "Low") |>
            select(EmotionalTrust, DistanceFinal))

print(paste0("Overall r(",corr_exp3$n-2,") = ",
             round(corr_exp3$r[1,2], 2),
             ", p=",
             round(corr_exp3$p[1,2], 4)))

print(paste0("High Quality r(",corr_exp3_high$n-2,") = ",
             round(corr_exp3_high$r[1,2], 2),
             ", p=",
             round(corr_exp3_high$p[1,2], 4)))

print(paste0("Low Quality r(",corr_exp3_low$n-2,") = ",
             round(corr_exp3_low$r[1,2], 2),
             ", p=",
             round(corr_exp3_low$p[1,2], 4)))

### AI Trust by Explanation and Quality Figure
fig_exp3_trust_explanation_quality <- exp3_data |>
  group_by(Quality, Explanation) |>
  summarize(n = n(),
            mean = mean(EmotionalTrust, na.rm = TRUE),
            se = sd(EmotionalTrust, na.rm = TRUE)/sqrt(n)) |>
  ggplot(aes(x = Quality,
             y = mean,
             color = Explanation,
             ymin = mean - 1.96 * se,
             ymax = mean + 1.96 * se)) +
    geom_hline(aes(yintercept = 1), color = "#D6D4CD") +
    geom_hline(aes(yintercept = 5), color = "#D6D4CD") +
    geom_pointrange(position = position_dodge(0.5)) +
    scale_color_manual(values = theme_paultol_colors(4)) +
    labs(y = "Trust",
         x = "AI Recommendation Quality",
         color = "AI Explanation") +
    ylim(1,5) +
    theme_jdc() +
    theme(axis.title.y = element_text(angle = 0),
          axis.ticks.y = element_blank(),
          legend.position = "right")

### AI Trust by Explanation Figure
fig_exp3_trust <- exp3_data |>
  group_by(Explanation) |>
  summarize(n = n(),
            mean = mean(EmotionalTrust, na.rm = TRUE),
            se = sd(EmotionalTrust, na.rm = TRUE)/sqrt(n)) |>
  ggplot(aes(x = Explanation,
             y = mean,
             color = Explanation,
             ymin = mean - 1.96 * se,
             ymax = mean + 1.96 * se)) +
    geom_hline(aes(yintercept = 1), color = "#D6D4CD") +
    geom_hline(aes(yintercept = 5), color = "#D6D4CD") +
    geom_pointrange(position = position_dodge(0.5)) +
    scale_color_manual(values = theme_paultol_colors(4)) +
    scale_x_discrete(labels = c("Global",
                                "What",
                                "What +\nWhy",
                                "What +\nWhy +\nHow")) +
    labs(y = "Trust",
         x = "AI Explanation",
         color = "") +
    ylim(1,5) +
    theme_jdc() +
    theme(axis.title.y = element_text(angle = 0),
          axis.ticks.y = element_blank(),
          legend.position = "right")


# Save the figure
ggsave(here::here("fig_exp3_trust.png"), fig_exp3_trust,
       width = 4, height = 3)


# Emotional trust by Quality
exp3_data |>
  group_by(Quality) |>
  summarize(mean_EmotionalTrust = mean(EmotionalTrust, na.rm = TRUE))

aov(EmotionalTrust ~ Quality, data = exp3_data) |> TukeyHSD()

# Emotional trust by Explanation
exp3_data |>
  group_by(Explanation) |>
  summarize(mean_EmotionalTrust = mean(EmotionalTrust, na.rm = TRUE))

aov(EmotionalTrust ~ Explanation, data = exp3_data) |> TukeyHSD()

```
